---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# stabiot

<!-- badges: start -->
[![R-CMD-check](https://github.com/kaigu1990/stabiot/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/kaigu1990/stabiot/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

The goal of `stabiot` is to assist statisticians and statistical programmers in using R functions and methods to oversee the outputs produced by SAS from outsourcing in clinical 
trials. The data sets would be ADaM format preferably, but they do not have to 
strictly follow the CDISC standards.

To guarantee accurate results, I prefer to wrap mature R package rather than rebuild statistical methods. Parts of statistics outputs are styled with `rtables`. For present, the completed sections are listed below.

- Simulation of sample size determination by Bayesian.
- Summarize Least-squares Means from models, such as ANCOVA and MMRM.
- Compute response rate, odds ratio with or without stratification, and corresponding 
confidence interval.
- Derive best overall response (confirmed or not confirmed BOR) per RECIST 1.1.
- Summarize survival analyses using `survival` package.

## Installation

You can install the development version of `stabiot` like so:

```{r gh-installation, eval = FALSE}
if (!require("devtools")) {
  install.packages("devtools")
}
devtools::install_github("kaigu1990/stabiot")
```
