---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# stabiot

<!-- badges: start -->
[![R-CMD-check](https://github.com/kaigu1990/stabiot/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/kaigu1990/stabiot/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

The goal of `stabiot` is to assist statisticians and programmers in using R functions 
and methods to oversee the outputs often produced by SAS from vendors in clinical 
trials. The data sets would be ADaM format preferably, but they do not have to 
follow the CDISC standard.

In order to ensure the quality and accuracy of the results, I prefer to wrap mature 
R package rather than rebuild the statistical methods. For now the completed sections 
are listed as shown below.

- Simulation of sample size determination by Bayesian.
- Summarize Least-squares Means from models, such as ANCOVA and MMRM.
- Computing response rate, odds ratio with or without stratification, and corresponding 
confidence interval.

## Installation

You can install the development version of `stabiot` like so:

```{r gh-installation, eval = FALSE}
if (!require("devtools")) {
  install.packages("devtools")
}
devtools::install_github("kaigu1990/stabiot")
```
